Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-09-05 paper/ms.tex
update ms
fix arxiv bibliography references

fix figure numbering

\begin{figure}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.43\textwidth]{f2completeness.pdf}
		\vspace{-0.2cm}
		\caption{
			{\bf Completeness of the TESS 2-minute data for late-K
      and early M dwarfs near the Sun, from Sectors 1-55.}  
      The orange dotted curve shows the number of stars in successive
      radial shells, each with a width of 10\,pc.  To be part of our selection function,
      these stars must meet the listed conditions: they must be red dwarf
      stars
      ($\bprp$>$1.5$; $M_{\rm G}$>4) amenable for TESS
      observations ($T$<16).  The blue solid curve shows the fraction
      of such stars with at least one sector of TESS 2-minute cadence
      data acquired between Sectors 1-55.
		}
			\vspace{-0.5cm}
		\label{fig:completeness}
	\end{center}
\end{figure}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f2.pdf}
		\vspace{-0.3cm}
		\caption{
      {\bf Validation plots used to classify CPVs}.  The complete figure
      set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable} is available in the online
      journal. {\bf For internal collaboration review:
      \url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
      Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
      The adopted period is given in the lower-right corner.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
      {\it c)}: DSS finder chart, with 21$''$ and 42$''$ radius
      circles for scale.  One TESS pixel has a full side length of
      21$''$.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram. The gray
      background denotes stars within 100\,pc from
      \citet{2021A&A...649A...6G}.
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities,
      calculated using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f3.pdf}
    \vspace{-0.3cm}
		\caption{
      {\bf CPVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CPVs in the high quality sample.  Gray are raw 2-minute data;
      black bins to 300 points per cycle.  Objects are ordered such
      that sources with the most TESS data available are on top (see
      Section~\ref{sec:catalog}).  Zero phase is chosen to correspond
      to minimum light.  Each panel is labeled by the TIC identifier,
      the TESS sector number, the period in hours, and the three-bit
      binarity flag from Table~\ref{tab:thetable}, which denotes Gaia
      DR3 \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
      \texttt{ruwe} outliers (bit 2), and stars with secondary TESS
      periods (bit 3). 
		}
		\label{fig:cqvs}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.95\textwidth]{f8.pdf}
		\vspace{-0.1cm}
		\caption{
			{\bf Properties of CPVs identified by our search}.
      CPVs are mostly pre-main-sequence M dwarfs, younger than
      $\approx$150 Myr, with rotation periods faster than
      $\approx$1\,day.  The \ngoods\ bona fide CPVs in
      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
      ambiguous CPV candidates are light blue circles.  Unresolved
      binaries (red circles) are objects for which the Gaia DR3 radial velocity
      scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
      and multiple photometric signals were present in the TESS light
      curve.  The top panels show the \nstarssearched\ target stars
      with 120-second cadence TESS data as the shaded gray background;
      darker regions correspond to a larger relative number of
      searched stars.  The lower-left panel compares the
      rotation--color distribution of CPVs against the rotation
      periods of K and M dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm c} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CPV periods, in
      units of hours.  Ages in the final panel are known from cluster
			membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f4.pdf}
		\vspace{-0.6cm}
		\caption{
			{\bf Evolution of CPV light curves over two years.}
			Out of the \ngoods\ CPVs in Figure~\ref{fig:cqvs}, 32 had
			120-second cadence TESS data available for a baseline of at
			least two years; the 27 brightest are shown here due to space
			constraints.  Each panel shows one sector of TESS data, and is
			phased to its deepest minimum in flux.  Each panel's title shows
			the TIC identifier and period in hours.  Text insets
			show the TESS sector numbers, which generally span two years, or
			at least 1{,}000 cycles.  The vertical scale is fixed across
			sectors to clarify shape changes.  Gray circles are raw 2-minute
			data; colored circles bin to 300 points per cycle. 
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f5.pdf}
		\vspace{-0.3cm}
		\caption{
      {\bf LP 12-502 (TIC~402980664) light curve}, where each time
      segment represents one TESS orbit.  Data were acquired in
      Sectors 18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.
      The light curve is binned to 15-minute intervals so that there
      are 96 points per day, and each point is connected by a line.
      Data gaps have nothing plotted.  The red vertical lines
      highlight apparently instantaneous state changes in the shape of
      the dip pattern.  
		}
		\label{fig:lplc}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f6.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Evolution of LP 12-502} ($P$=18.5611\,h) at fixed period and
      epoch over three years.  Each panel shows one (averaged) TESS
			orbit; small text denotes relative cycle number.  There are 200
			binned black points per cycle.  The TESS pointing law dictates
			the large time gaps between cycles 64-248, 315-1233, and
			1264-1410; larger gaps tend to yield larger shape changes.  The
			dips usually evolve over tens to hundreds of cycles.  However
			cycles 1233-1264 show a dip that switched from a depth and
			duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than one
			cycle (cf.~Figure~\ref{fig:lplc}).
		}
		\label{fig:lp}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f7a.pdf}
			\includegraphics[width=0.48\textwidth]{f7b.pdf}
		}
		\vspace{-0.2cm}

		\subfloat{
			\includegraphics[width=0.48\textwidth]{f7d.pdf}
			\includegraphics[width=0.48\textwidth]{f7c.pdf}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
    {\bf River plots of the LP 12-502 light curve}, showing (clockwise
    from top-left) Sectors 18-19, 25-26, 53, and 58-59.  A
    two-harmonic sinusoid has been subtracted to highlight the sharp
    dips.  
    A fixed period and phase are adopted for all sectors; the dips
    across all observations are bounded by $\phi \in [-0.35,0.35]$.
    In Sectors 25-26 (cycles 248-315), periods are visible at
    the fundamental period of 18.5611\,hr, as well as at faster
    ($\phi$$\approx$0-0.07) and slower ($\phi$$\approx$0.25-0.27)
    relative periods based on the presence of blue dips with distinct
    slopes.  Multiple simultaneous periods are also visible in Sector
    53 (cycles 1234-1263) and Sectors 58-59 (cycles 1411-1479).  White
    chunks denote missing data.
    The state changes noted with red markers in Figure~\ref{fig:lplc} occur in
    cycles 261, 309, and 1241.
	}
	\label{fig:lpriver0}
\end{figure*}

@@

\begin{figure}[!th]
	\begin{center}
		\centering
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f9a.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f9b.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f9c.pdf}
		}

@@

\acknowledgments
LGB is grateful for support from the Heising-Simons 51~Pegasi~b
Fellowship.  This paper benefited from conversations between the
authors and G.~Laughlin, A.~Mann, J.~Spake, and B.~Draine.  The paper
also relied on data collected by the TESS mission, which are available
from the Mikulski Archive for Space Telescopes (MAST).  The specific
120-second cadence observations can be accessed via
DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
Funding for the TESS mission is provided by NASA’s Science Mission
Directorate.  TIC 402980664 in particular was observed at 120-second
cadence thanks to the TESS Guest Investigator programs G022252 (PI:
J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman;
Sector 53).  LGB is also grateful for the assistance of S.~Yee,
L.~Weiss, H.~Isaacson, and A.~Howard in acquiring and analyzing the
HIRES spectra.

@@

\software{
  %\texttt{arviz} \citep{arviz_2019},
  %\texttt{altaipony} \citep{ilin_flares_2021},
  \texttt{astrobase} \citep{2021zndo...1011188B},
  %\texttt{astroplan} \citep{astroplan2018},
	%\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  %\texttt{astropy} \citep{astropy_2018},
 % \texttt{astroquery} \citep{astroquery_2018},
  \texttt{astropy} \citep{astropy_2013,astropy_2018,astropy_2022},
  %\texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  %\texttt{ceres} \citep{brahm_2017_ceres},
  %\texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  %\texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  %\texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  %dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
  % 	exoplanet:theano},
	%\texttt{gala} \citep{gala,PriceWhelan_2017_gala_zenodo},
	%\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  %\texttt{IPython} \citep{perez_2007},
	%\texttt{isochrones} \citep{morton_2015_isochrones},
	\texttt{lightkurve} \citep{2018ascl.soft12013L},
  %\texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  %\texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{2020Natur.585..357H}, 
  %\texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{daniel_serven_2018_1208723},
  %\texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{2020NatMe..17..261V},
  \texttt{TESS-point}  \citep{2020ascl.soft03001B},
  %\texttt{tesscut} \citep{brasseur_astrocut_2019},
  %\texttt{unpopular} \citep{hattorio_2021_cpm},
  %\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  %\texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
\

\facilities{
 	{\it Astrometry}:
		Gaia \citep{2018A&A...616A...1G,2022arXiv220800211G}.
 	{\it Imaging}:
    Second Generation Digitized Sky Survey. %,
    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
		%Keck:II~(NIRC2).
		%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
		%Gemini:North~(`Alopeke; \citealt{scott_nessi_2018,scott_twin_2021}.
 	{\it Spectroscopy}:
		%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
		%PFS ({\bf CITE}),
		%Tillinghast:1.5m~(TRES).
		%MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
		%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
		%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
		Keck:I~(HIRES; \citealt{1994SPIE.2198..362V}).
		%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
 	  %Euler1.2m~(CORALIE),
 	  %ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
		%ASTEP:0.40$\,$m (ASTEP400),
		%CTIO:1.0m (Y4KCam),
		%Danish 1.54m Telescope,
		%El Sauce:0.356$\,$m,
		%Elizabeth 1.0m at SAAO,
		%Euler1.2m (EulerCam),
		%Kepler,
		%Magellan:Baade (MagIC),
		%Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
		%MuSCAT3 \citep{Narita_2020},
		%NTT,
		%SOAR (SOI),
 	  TESS \citep{2015JATIS...1a4003R},
		%TRAPPIST \citep{jehin_trappist_2011},
		%VLT:Antu (FORS2).
		%ZTF.
  {\it Broadband photometry}:
    2MASS \citep{2006AJ....131.1163S},
    APASS \citep{2016yCat.2336....0H},
		Gaia \citep{2018A&A...616A...1G,2022arXiv220800211G},
    SDSS \citep{2000AJ....120.1579Y},
    WISE \citep{2010AJ....140.1868W}.
}

\bibliographystyle{yahapj}                            
\bibliography{bibliography}

>>>>

\begin{figure}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.43\textwidth]{f2.pdf}
		\vspace{-0.2cm}
		\caption{
			{\bf Completeness of the TESS 2-minute data for late-K
      and early M dwarfs near the Sun, from Sectors 1-55.}  
      The orange dotted curve shows the number of stars in successive
      radial shells, each with a width of 10\,pc.  To be part of our selection function,
      these stars must meet the listed conditions: they must be red dwarf
      stars
      ($\bprp$>$1.5$; $M_{\rm G}$>4) amenable for TESS
      observations ($T$<16).  The blue solid curve shows the fraction
      of such stars with at least one sector of TESS 2-minute cadence
      data acquired between Sectors 1-55.
		}
			\vspace{-0.5cm}
		\label{fig:completeness}
	\end{center}
\end{figure}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f3.pdf}
		\vspace{-0.3cm}
		\caption{
      {\bf Validation plots used to classify CPVs}.  The complete figure
      set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable} is available in the online
      journal. {\bf For internal collaboration review:
      \url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
      Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
      The adopted period is given in the lower-right corner.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
      {\it c)}: DSS finder chart, with 21$''$ and 42$''$ radius
      circles for scale.  One TESS pixel has a full side length of
      21$''$.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram. The gray
      background denotes stars within 100\,pc from
      \citet{2021A&A...649A...6G}.
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities,
      calculated using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f4.pdf}
    \vspace{-0.3cm}
		\caption{
      {\bf CPVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CPVs in the high quality sample.  Gray are raw 2-minute data;
      black bins to 300 points per cycle.  Objects are ordered such
      that sources with the most TESS data available are on top (see
      Section~\ref{sec:catalog}).  Zero phase is chosen to correspond
      to minimum light.  Each panel is labeled by the TIC identifier,
      the TESS sector number, the period in hours, and the three-bit
      binarity flag from Table~\ref{tab:thetable}, which denotes Gaia
      DR3 \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
      \texttt{ruwe} outliers (bit 2), and stars with secondary TESS
      periods (bit 3). 
		}
		\label{fig:cqvs}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.95\textwidth]{f5.pdf}
		\vspace{-0.1cm}
		\caption{
			{\bf Properties of CPVs identified by our search}.
      CPVs are mostly pre-main-sequence M dwarfs, younger than
      $\approx$150 Myr, with rotation periods faster than
      $\approx$1\,day.  The \ngoods\ bona fide CPVs in
      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
      ambiguous CPV candidates are light blue circles.  Unresolved
      binaries (red circles) are objects for which the Gaia DR3 radial velocity
      scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
      and multiple photometric signals were present in the TESS light
      curve.  The top panels show the \nstarssearched\ target stars
      with 120-second cadence TESS data as the shaded gray background;
      darker regions correspond to a larger relative number of
      searched stars.  The lower-left panel compares the
      rotation--color distribution of CPVs against the rotation
      periods of K and M dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm c} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CPV periods, in
      units of hours.  Ages in the final panel are known from cluster
			membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f6.pdf}
		\vspace{-0.6cm}
		\caption{
			{\bf Evolution of CPV light curves over two years.}
			Out of the \ngoods\ CPVs in Figure~\ref{fig:cqvs}, 32 had
			120-second cadence TESS data available for a baseline of at
			least two years; the 27 brightest are shown here due to space
			constraints.  Each panel shows one sector of TESS data, and is
			phased to its deepest minimum in flux.  Each panel's title shows
			the TIC identifier and period in hours.  Text insets
			show the TESS sector numbers, which generally span two years, or
			at least 1{,}000 cycles.  The vertical scale is fixed across
			sectors to clarify shape changes.  Gray circles are raw 2-minute
			data; colored circles bin to 300 points per cycle. 
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f7.pdf}
		\vspace{-0.3cm}
		\caption{
      {\bf LP 12-502 (TIC~402980664) light curve}, where each time
      segment represents one TESS orbit.  Data were acquired in
      Sectors 18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.
      The light curve is binned to 15-minute intervals so that there
      are 96 points per day, and each point is connected by a line.
      Data gaps have nothing plotted.  The red vertical lines
      highlight apparently instantaneous state changes in the shape of
      the dip pattern.  
		}
		\label{fig:lplc}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f8.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Evolution of LP 12-502} ($P$=18.5611\,h) at fixed period and
      epoch over three years.  Each panel shows one (averaged) TESS
			orbit; small text denotes relative cycle number.  There are 200
			binned black points per cycle.  The TESS pointing law dictates
			the large time gaps between cycles 64-248, 315-1233, and
			1264-1410; larger gaps tend to yield larger shape changes.  The
			dips usually evolve over tens to hundreds of cycles.  However
			cycles 1233-1264 show a dip that switched from a depth and
			duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than one
			cycle (cf.~Figure~\ref{fig:lplc}).
		}
		\label{fig:lp}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f9a.pdf}
			\includegraphics[width=0.48\textwidth]{f9b.pdf}
		}
		\vspace{-0.2cm}

		\subfloat{
			\includegraphics[width=0.48\textwidth]{f9d.pdf}
			\includegraphics[width=0.48\textwidth]{f9c.pdf}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
    {\bf River plots of the LP 12-502 light curve}, showing (clockwise
    from top-left) Sectors 18-19, 25-26, 53, and 58-59.  A
    two-harmonic sinusoid has been subtracted to highlight the sharp
    dips.  
    A fixed period and phase are adopted for all sectors; the dips
    across all observations are bounded by $\phi \in [-0.35,0.35]$.
    In Sectors 25-26 (cycles 248-315), periods are visible at
    the fundamental period of 18.5611\,hr, as well as at faster
    ($\phi$$\approx$0-0.07) and slower ($\phi$$\approx$0.25-0.27)
    relative periods based on the presence of blue dips with distinct
    slopes.  Multiple simultaneous periods are also visible in Sector
    53 (cycles 1234-1263) and Sectors 58-59 (cycles 1411-1479).  White
    chunks denote missing data.
    The state changes noted with red markers in Figure~\ref{fig:lplc} occur in
    cycles 261, 309, and 1241.
	}
	\label{fig:lpriver0}
\end{figure*}

@@

\begin{figure}[!th]
	\begin{center}
		\centering
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f10a.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f10b.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f10c.pdf}
		}

@@

\acknowledgments
LGB is grateful for support from the Heising-Simons 51~Pegasi~b
Fellowship, and for helpful conversations with
J.~Spake, A.~Mann, G.~Laughlin, and B.~Draine.  
We are also grateful for the assistance of S.~Yee,
L.~Weiss, H.~Isaacson, and A.~Howard in acquiring and reducing the
HIRES spectra.
This paper relied primarily on data collected by the TESS mission; the specific
120-second cadence observations can be accessed via
DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
Funding for the TESS mission is provided by NASA’s Science Mission
Directorate.  
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, and J.~Jenkins) and the many TESS team members for their efforts to make the mission a continued success. 
TIC 402980664 in particular was observed at 120-second
cadence thanks to the TESS Guest Investigator programs G022252 (PI:
J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman;
Sector 53).

@@

\software{
  %\texttt{arviz} \citep{arviz_2019},
  %\texttt{altaipony} \citep{ilin_flares_2021},
  \texttt{astrobase} \citep{2021zndo...1011188B},
  %\texttt{astroplan} \citep{astroplan2018},
	%\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  %\texttt{astropy} \citep{astropy_2018},
 % \texttt{astroquery} \citep{astroquery_2018},
  \texttt{astropy} \citep{astropy_2013,astropy_2018,astropy_2022},
  %\texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  %\texttt{ceres} \citep{brahm_2017_ceres},
  %\texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  %\texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  %\texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  %dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
  % 	exoplanet:theano},
	%\texttt{gala} \citep{gala,PriceWhelan_2017_gala_zenodo},
	%\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  %\texttt{IPython} \citep{perez_2007},
	%\texttt{isochrones} \citep{morton_2015_isochrones},
	\texttt{lightkurve} \citep{2018ascl.soft12013L},
  %\texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  %\texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{2020Natur.585..357H}, 
  %\texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{daniel_serven_2018_1208723},
  %\texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{2020NatMe..17..261V},
  \texttt{TESS-point}  \citep{2020ascl.soft03001B},
  %\texttt{tesscut} \citep{brasseur_astrocut_2019},
  %\texttt{unpopular} \citep{hattorio_2021_cpm},
  %\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  %\texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{2019AJ....158..143H}.
}
\

\facilities{
 	{\it Astrometry}:
		Gaia \citep{2018A&A...616A...1G,2023A&A...674A...1G}.
 	{\it Imaging}:
    Second Generation Digitized Sky Survey. %,
    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
		%Keck:II~(NIRC2).
		%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
		%Gemini:North~(`Alopeke; \citealt{scott_nessi_2018,scott_twin_2021}.
 	{\it Spectroscopy}:
		%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
		%PFS ({\bf CITE}),
		%Tillinghast:1.5m~(TRES).
		%MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
		%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
		%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
		Keck:I~(HIRES; \citealt{1994SPIE.2198..362V}).
		%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
 	  %Euler1.2m~(CORALIE),
 	  %ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
		%ASTEP:0.40$\,$m (ASTEP400),
		%CTIO:1.0m (Y4KCam),
		%Danish 1.54m Telescope,
		%El Sauce:0.356$\,$m,
		%Elizabeth 1.0m at SAAO,
		%Euler1.2m (EulerCam),
		%Kepler,
		%Magellan:Baade (MagIC),
		%Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
		%MuSCAT3 \citep{Narita_2020},
		%NTT,
		%SOAR (SOI),
 	  TESS \citep{2015JATIS...1a4003R},
		%TRAPPIST \citep{jehin_trappist_2011},
		%VLT:Antu (FORS2).
		%ZTF.
  {\it Broadband photometry}:
    2MASS \citep{2006AJ....131.1163S},
    APASS \citep{2016yCat.2336....0H},
		Gaia \citep{2018A&A...616A...1G,2023A&A...674A...1G},
    SDSS \citep{2000AJ....120.1579Y},
    WISE \citep{2010AJ....140.1868W}.
}

\clearpage

\def\bibfont{\footnotesize}
\bibliographystyle{yahapj}                           
\renewcommand*{\bibfont}{\footnotesize} 
{\footnotesize \bibliography{bibliography} }
